\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Nazran Khondokar} \\ \vspace{1pt}
    Dhaka, Bangladesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +880-1714-516763 ~ \href{mailto:nazran91@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nazran91@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/nazran91/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/nazran91}}  ~
    \href{https://github.com/NazranKhondokar/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/NazranKhondokar}}
    \vspace{-8pt}
\end{center}

\section{Career Summary}
6+ years of expertise in Spring Boot, Java, SQL, and Flutter, building scalable microservices, APIs, and real-time systems. Proven impact in fintech, e-commerce, and education tech, optimizing performance and integrating big data & cloud solutions. Passionate about automotive software & analytics, leveraging AI, and IoT.
            

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, TypeScrpt, Dart, Python, XML, C, SQL, Kotlin.} \\
     \textbf{Frameworks \& Libraries}{: Spring Boot, Servlet, Hibernate, RabbitMQ, Kafka, Angular, Flutter, Android.}\\
     \textbf{Database}{: PostgreSQL, Microsoft SQL Server, MySQL, Redis, SQLite, RoomDB, Firestore.}\\
     \textbf{Testing}{: JUnit, Mockito}
     \textbf{Identity \& Access Management}{: Keycloak.}\\
     \textbf{Encryption/Decryption}{: AES 256.}
     \textbf{AWS}{: DynamoDB, EC2, S3.}\\
     \textbf{Build tool}{: Maven, Gradle.}
     \textbf{Project management system}{: JIRA, Open Project, Trello, Asana.}\\
     \textbf{Environment}{: IntelliJ IDEA, PyCharm, Netbeans, Android Studio, XCode, Eclipse, DBeaver.}\\
     \textbf{Operating System}{: Mac OS, Windows, Linux.}
     \textbf{Server}{: Docker, Netflix Eureka, CentOS, Ubuntu.}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.linkedin.com/company/nexalinx/}{Nexalinx}}{Nov 2024 -- Present}
      {Senior Software Engineer}{Dhaka, BD}
      \resumeItemListStart
        \resumeItem{Developed the backend for the Bitcoin Canvas mobile app using Spring Boot and PostgreSQL, ensuring scalability. Collaborated with cross-functional teams to optimize API performance and enhance system reliability.}
        \resumeItem{Designed and implemented REST APIs for core modules, including authentication, onboarding, and personalized dashboards. Delivered key features such as subscription management, user preferences, and transaction tracking. }
        \resumeItem{Integrated real-time Bitcoin market data and analytics via third-party APIs, enhancing user experience with live updates. Supported advanced market tools like the DCA Simulator and price change alerts for investment planning.}
      \resumeItemListEnd
      \resumeSubheading
      {\href{https://www.linkedin.com/company/ethics-advance-technology-limited./}{Ethics Advance Technology Limited}}{May 2021 -- Oct 2024}
      {Software Engineer}{Dhaka, BD}
      \resumeItemListStart
        \resumeItem{Engaged in the largest Integrated Education Information Management System in Bangladesh related to students, teachers, and institutions from class VI to XII data with micro-service architecture.}
        \resumeItem{Among 34 services, I am responsible for 4 services generating flow/class diagrams, SRS, and designing ERD.}
        \resumeItem{I built the services using Spring boot, SQL server, Kafka, Socket, Docker, Jasper Report, ELK, Redis, KeyCloak, etc. Among them, 2 are used country-wide. Also provide live support on different services.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://www.linkedin.com/company/rokomari-com/}{Rokomari}}{Jun 2019 -- May 2021}
      {Software Engineer}{Dhaka, BD}
      \resumeItemListStart
        \resumeItem{Built a service for the telemarketing team  using Angular, Spring Boot and MySQL where an admin can assign different customers to different types of agents then agents call customers through the Rokomari telemarketing android app.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Development of an e-commerce mobile application for iOS/Android using Dart and the Flutter framework from scratch.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.linkedin.com/company/uumoo/}{Uumoo Limited}}{May 2018 -- May 2019}
      {Full Stack App Developer}{Dhaka, BD}
      \resumeItemListStart
        \resumeItem{Designed a FinTech service from scratch by analyzing requirements.}
        \resumeItem{Development \& maintenance of a payment app that enables users to exchange, trade and conduct commerce.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.linkedin.com/company/maxxitsolution/}{Max IT}}{Oct 2017 - Apr 2018}
      {Android Application Developer}{Dhaka, BD}
      \resumeItemListStart
        \resumeItem{Configured admin panel using Laravel \& built e-commerce, audio/video call app using Android, AppRTC, Firebase.}
        \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in Android.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.linkedin.com/company/infinity-flame-soft/}{Infinity Flame Soft}}{Oct 2016 - Sep 2017}
      {Trainer, Android Application Development}{Sylhet, BD}
    
  \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
          
      \resumeProjectHeading
          {\href{https://drive.google.com/file/d/1LBLfv-0ZpTDAU-O6mhQf8z5ERY96lPCn/preview}{\textbf{“Non-Govt Teacher Registration Certificate Authority” result process and allocation}}}{December 2022}
          \resumeItemListStart
            \resumeItem{Built an async process to upload certified results from Excel sheets using the procedure.}
            \resumeItem{Generated a merit list with an optimized query for all batches.}
            \resumeItem{Provided a panel to submit subject and designation-wise teacher requisitions from the institute through payment.}
            \resumeItem{Taking the choice from applicants, generate the result to allocate an applicant through the seat allocation algorithm.}
            \resumeItem{Converted complicated govt monthly pay order rules for each designation into ERD \& validated them to allocate.}
          \resumeItemListEnd 
          \vspace{-5pt}
          
          \resumeProjectHeading
          {\href{https://drive.google.com/file/d/1T99QKmyLxcL_5ZhCJD0mjvOavD9YCTEh/preview}{\textbf{“E-Survey” an annual survey report of 40K institutes}}}{April 2022}
          \resumeItemListStart
            \resumeItem{Designed circular creation panel with date range region-wise to submit institutional data by admin.}
            \resumeItem{Institute-wise dynamic table generation to submit teacher, student, employee, degree, etc information.}
            \resumeItem{Provided a multi-type admin dashboard to review the institutional data with forward and backward mechanisms.}
          \resumeItemListEnd 
           \vspace{-13pt}

          \resumeProjectHeading
          {\href{https://drive.google.com/file/d/1vD1i5SNvjEfylsUq-Ny00h5hgWqQo8LT/preview}{\textbf{“Educational Institute Identification Number” generation}}}{September 2021}
          \resumeItemListStart
            \resumeItem{Provided the registration panel with valid credentials and the application panel to request for “Institute Identification Number” with valid Govt permission documents.}
            \resumeItem{Customized review configuration \& after review notification and email triggered.}
          \resumeItemListEnd 
           \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{Rokomari Telemarketing Service} $|$ \emph{Spring Security, Data JPA, MySQL, Angular}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a Telemarketing call management service using Spring Boot to manage customer care calls.}
            \resumeItem{Used Angular to create a UI that supports actions such as uploading users, agent registration, assigning agents etc.}
          \resumeItemListEnd 
           \vspace{-13pt}

           \resumeProjectHeading
          {\href{https://apps.apple.com/us/app/rokomari-trusted-online-store/id1493045502}{\textbf{Rokomari (Android \& iOS)} $|$ \emph{Flutter, Firebase, Facebook SDK, Payment Gateway, Bloc}}}{November 2019}
          \resumeItemListStart
            \resumeItem{Built the most complicated product browse page UI, filtering, sorting, and pagination with Rest API integration.}
            \resumeItem{Built user account section UI \& API integration such as user account update, avatar change, phone number \& password change with OTP, orders, order tracking, product reviews \& ratings, create a favorite list with multi products, delete the list, and create a wish list etc.}
            \resumeItem{Built authorization section such as user registration, login, forgot \& change password.}
            \resumeItem{Added crashlytics \& push notifications with Firebase and OneSinal.}
            \resumeItem{Added marketing Facebook SDK \& publish the app to the Apple app store.}
          \resumeItemListEnd 
           \vspace{-13pt}
        
           
          \resumeProjectHeading
          {\href{https://drive.google.com/file/d/1UmFqvvCmJASvv_Hj4EYwOrWUpg7c4M52/preview}{\textbf{UUMOO Pocket \& Drawer} $|$ \emph{QR, OCR, AES/RSA, Room DB, Retrofit, Proguard, Google Map clustering}}}{July 2018}
          \resumeItemListStart
            \resumeItem{Built apps according to commercial dynamic UI conversion using XML, Java.}
            \resumeItem {Worked with QR Code, OCR (Firebase ML Kit), android security (AES/RSA).}
            \resumeItem {Stored local data with Room \& Load server data with Volley, Retrofit.}
            \resumeItem {Push data handling to notify the app \& custom Google Maps with clustering.}
            \resumeItem {Detect user location and find available UUMOO at different distances using REST API.}
            \resumeItem {Used ProGuard for obfuscation and making it difficult to reverse engineering}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          \resumeProjectHeading
          {\href{https://play.google.com/store/apps/details?id=net.maxitbd.takshal}{\textbf{Takshal} $|$ \emph{Java, Android, Laravel, Facebook auth}}}{October 2017}
          \resumeItemListStart
            \resumeItem{Built \& maintained an e-commerce app where users are going to buy the most exclusive Brand watches.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.sust.edu/}{\textbf{Shahjalal University of Science and Technology}}}{Sylhet, BD}
      {Bachelor of Science in Computer Science and Engineering;  CGPA: 3.31 out of 4}{Jan. 2013 -- Jan. 2018}
  \resumeSubHeadingListEnd
\vspace{1pt}

%-----------INVOLVEMENT---------------
\section{Programming Contest}
            \resumeItemListStart
                \resumeItem{Got a good position on Islamic University of Technology 5th \& 6th ICT Fest Programming Contest 2014 \& 2015. Also on State University National Collegiate Programming Contest 2014.}
                \resumeItem{350+ ACM problem solving on 
                {\href{https://uhunt.onlinejudge.org/id/249088}{\raisebox{-0.2\height}\ \underline{\textbf{Uva}}}}, Codeforces.}
            \resumeItemListEnd
\vspace{-10pt}

%-----------Training---------------
\section{Training}
  \resumeItemListStart
    \resumeItem
      {\href{https://gameapp.gov.bd/}{\raisebox{-0.2\height}\ \underline{\textbf{Training of Trainers}}} (AIUB - 2018) :
      {Skill Development for Mobile Game and Application}}
        \resumeItem
        {\textbf{EATL Mobile App Development Training} (SUST - 2015) : {Android Development Course}}
        \resumeItem
      {\textbf{Advanced Mobile Game Development \& Graphics Design} (LICT - 2016) :
      {Unity3d and Blender Learning}}
        \resumeItem
      {\textbf{Bangladesh Android Study Jam} (SUST - 2015) :
      {Udacity Android Development Course}}
  \resumeItemListEnd
\vspace{-10pt}

%-----------Training---------------
\section{Language}
  \resumeItemListStart
    \resumeItem
      {Bengali as mother tongue, fluent in English}
  \resumeItemListEnd
  
\end{document}
